The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-11-09 Moving temporal window - HESS/template.tex
Killing some tables.

Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated on the original archive (Tables \ref{table:performance}) and will be used thereafter.

The impact of the change in the archive length is summarized in Table \ref{table:loss_reduction} for both 2Z and 2Z-2MI methods. As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change. This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.

@@

The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length. The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method. The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant. Moreover, it requires no additional predictor. No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.

@@

After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}). Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease (not shown). More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method. The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.

@@

The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.

@@

A proportional distribution is certainly the simplest approach that can be performed. It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig. \ref{fig:illustration_disaggregation}). When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_MTW}) and was even below the conventional method without MTW (Table \ref{table:loss_reduction}). The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.

@@

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
	\caption{Performance score (CRPS, \%) of the analog method on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e. 1961-2008, (yellow) the reduced archive, i.e. 1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibration of the AM parameters with the MTW.}
	\label{fig:plots_CRPSS_2Z}
\end{figure}

@@

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
			& $N_{1}$ & CRPSS & $N_{1}$ & $N_{2}$ & CRPSS \\ 
			\hline
			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:performance}
\end{table}

\begin{table}[htb]
	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
			\hline
			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:loss_reduction}
\end{table}

\begin{table}[htb]
	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_MTW}
\end{table}

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), using the MTW approach.}
	\begin{center}
		\begin{tabular}{l c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{1}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& $N_{1}$ & $N_{1}$ & $N_{2}$ \\ 
			\hline
			Ulrichen & 50 & 110 & 35 \\
			Zermatt & 55 & 80 & 30 \\
			Visp & 55 & 135 & 35 \\
			Montana & 55 & 110 & 40 \\
			Sion & 55 & 140 & 50 \\
			Aigle & 75 & 135 & 45 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:nb_analogs_new}
\end{table}

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_recalibration}
\end{table}

>>>>

Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated on the original archive (Tables \ref{table:analog_nb}) and will be used thereafter.

The impact of the change in the archive length is visible in Fig. \ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig. \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method. As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change. This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.

@@

The new performance scores are provided in Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, along with the differences regarding the conventional method with the same archive length. The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method. The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant. Moreover, it requires no additional predictor. No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.

@@

After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:analog_nb}). Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease (not shown). More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method. The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.

@@

The values of the CRPSS scores for both methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.

@@

A proportional distribution is certainly the simplest approach that can be performed. It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig. \ref{fig:illustration_disaggregation}). When using this reconstructed time series on the shorter period, the method performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}). The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.

@@

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
	\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e. 1961-2008, (yellow) the reduced archive, i.e. 1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibrated parameters of the AM with the MTW.}
	\label{fig:plots_CRPSS_2Z}
\end{figure}

@@

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive (Standard) and after recalibration using the MTW (MTW-r).}
	\begin{center}
		\begin{tabular}{l c c c c c c }
			\hline
			\multirow{3}{*}{Station} & \multicolumn{3}{c}{Standard} & \multicolumn{3}{c}{MTW-r} \\
			& 2Z & \multicolumn{2}{c}{2Z-2MI} & 2Z & \multicolumn{2}{c}{2Z-2MI}\\
			& $N_{1}$ & $N_{1}$ & $N_{2}$ & $N_{1}$ & $N_{1}$ & $N_{2}$\\ 
			\hline
			Ulrichen & 40 & 60 & 25 & 50 & 110 & 35\\
			Zermatt & 35 & 55 & 25 & 55 & 80 & 30\\
			Visp & 30 & 45 & 25 & 55 & 135 & 35\\
			Montana & 40 & 55 & 30 & 55 & 110 & 40\\
			Sion & 40 & 90 & 30 & 55 & 140 & 50\\
			Aigle & 50 & 100 & 35 & 75 & 135 & 45\\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:analog_nb}
\end{table}
